A holomorphic approach to membranes and fivebranes

### 2022-06-15 fivebranes/twisted.tex
updated sugra at boundary of ads

\documentclass[11pt]{amsart}%

%\usepackage{../macros-master}
\usepackage{macros-fivebrane}

\begin{document}

@@

@@

We begin by describing the complement of the zero section
\[
\R\oplus V \setminus 0\times Z
\]. Note that $\R \times X$ is equipped with a natural transverseley-holomorphic foliation. That is, there is a rank 1 subbundle $\R\subset \R\oplus V$ together with a complex structure on the quotient. Accordingly, we may choose as fiber coordinates $t, w_{1}, w_{2}, \bar w_{1}, \bar w_{2}$ and a fiberwise partially hermitian metric $h$. Explicitly, the corresponding norm is given by
\begin{align*}
 \pi:  \R\times X & \to \R_{+} \\
  (t, w_{i}, \bar{w_{i}}, p)& \mapsto t^{2} + |w_{1}|^{2}+|w_{2}|^{2}
\end{align*}
Letting $p : \R\times X \to Z$, we have an $S^{4}$-bundle $(\pi, p) : \R\times X - Z \to \R_{>0}\times Z$. The vertical tangent bundle of this $S^{4}$ bundle inherits a natural subbundle coming from the THF structure of the ambient manifold; the fibers of this subbundle equip

>>>>

%\documentclass[11pt]{amsart}%

%\usepackage{../macros-master}
%\usepackage{macros-fivebrane}

%\begin{document}

@@

\subsection{Twisted Membranes}
\surya{add}

@@

We begin by describing the complement of the zero section
\[
M = \R\oplus V \setminus 0\times Z.
\]

Note that $\R \times X$ is equipped with a natural transverseley-holomorphic foliation - the complexified tangent bundle decomposes as $T_{\R}\oplus T_{Z}\oplus \bar T_{Z}$. Accordingly, we may choose as fiber coordinates $t, w_{1}, w_{2}, \bar w_{1}, \bar w_{2}$ and a fiberwise partially hermitian metric $h$. Explicitly, the corresponding norm is given by
\begin{align*}
 \pi:  \R\times X & \to \R_{+} \\
  (t, w_{i}, \bar{w_{i}}, p)& \mapsto t^{2} + |w_{1}|^{2}+|w_{2}|^{2}
\end{align*}
Letting $p : \R\times X \to Z$, we have an $S^{4}$-bundle $(\pi, p) : \R\times X - Z \to \R_{>0}\times Z$. Let $V_{M}$ denote the vertical tangent bundle to $(\pi, p)$, which we view as a subbundle of the real tangent bundle $T_{M}$. The complexification $V_{M}^{\C}$ inherits some natural subbundles coming from the ambient THF structure. Indeed, letting $\iota : M \to \R\times X$ denote the standard inclusion, we may consider the pair
\[
  V_{M}\cap \iota^{*} T_{\R}, \ \ \ \ \ V\cap \iota^{*} T_{Z}.
\]

The fibers of the composition $V_{M}\to M\to \R_{+}\times Z$ are copies of the tangent bundle of $S^{4}$, and the corresponding fibers of $V_{M}$ are subbundles of $TS^{4}$ that equip the fiber 4-spheres with a generalized Cauchy-Riemann structure. \surya{CITE}

We wish to describe the pushforward $(\pi, p)_{*}\cL_{sugra}$. The underlying sheaf of cochain complexes is given by

\[
\Omega^{\bullet}(\R_{+})\otimes \left ( \begin{tikzcd}
\ul{\rm even} & \ul{\rm odd} \\
\PV^{1,\bu}(Z) \ar[r, "\del_{\Omega}"] & \PV^{0,\bu}(Z)\\
\Omega^{0,\bu}(Z) & \Omega^{1,\bu}(Z) \ar[l, "\del"]
\end{tikzcd}
 \right ) \otimes CR (S^{4}).
\]

Here $CR (S^{4})$ denotes the cohomology of the tangential Cauchy-Riemann complex of $S^{4}$ \surya{CITE}, equipped with the above Cauchy-Riemann structure. Its computation is facilitated by the following lemma:

\begin{lem}
  Let $\R^{d}\times \C^{n}$ be an affine THF manifold, and choose a partial hermitian metric. Let $S^{d+2n-1}$ denote the corresponding unit sphere, equipped with its standard generalized Cauchy-Riemann structure. Then there is a quasi-isomorphism

  \[CR (S^{n+2d-1})\cong \cA^{\bu;\bu}\left ( (\R^{d}\times \C^{n})\setminus 0 \right )\]

  where the right-hand-side denotes the Dolbeault-deRham complex.
\end{lem}

The cohomology of the Dolbeault-deRham complex of $\R\times \C^{2}$ is easy to describe.
